### 2019-12-24 Statistical Methods/08_Regression.rmd
statistical methods
statistical methods

### 8.9
### 8.10

>>>>

### 8.9

In exercise 5, what would be the least squares estimate of the cancer rate given a solar radiation of 600?

```{r, echo = T, fig.width=8, fig.height=3.5}
dat <- data.table::fread(paste0(data.dir, "cancer_rate_dat.txt"), fill = T, sep = "&")

ggplot(dat, aes(calories, Rate)) +
   geom_point() +
   geom_smooth(method = "lm")

fit <- lm(Rate ~ calories, data = dat)

coef(fit)

39.99 -0.037*600
```
Why might this be unreasonable?

_Because 600 is outside of the bounds of seen values (extrapolation)._

### 8.10
